\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-16 paper.tex
Modifique y respondi algunas observaciones

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\usepackage{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}}\notaL{\sout{Indica el voltaje y la
    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}
    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
  fuente de voltaje}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

  \nabla^2\varphi=-4\pi q_0\delta(\bm r-\bm r_0),

@@

  \varphi(x,y,0)=0,

@@

\notaL{\sout{ref}}. The potential within the electrolytic cell coincides the
the field within an infinite vacuum containing the point charge
This problem may be solved readily using image charge theory
\notaL{ref}. The potential within the electrolytic cell coincides

@@

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique \cite{T3,T4,T5}\notaL{\sout{ref}}, which yields
 two rapidly convergingseries, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which there are no
real nor image charges, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors, and then sum over the charges that form the basis
of the 2D {\em crystal} plane and finally sum over all the
 planes \cite{T6,T7} \notaL{\sout{ref}}.
using the Ewald summation technique \notaL{ref}, which yields two rapidly converging
series, one in real space and another one in reciprocal space.
Nevertheless, as we have to evaluate the potential and the field on
the bottom of the cell to obtain the current density which attacks the
surface of the sample, and as there are no
real nor image charges there, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors, we then sum over the charges that form the basis
of the 2D {\em crystal} plane and we finally sum over all the planes \notaL{ref}.

We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{_{\bm G}}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{_{\bm G}}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{_{\bm G}}(z)-G^2\phi_{_{\bm G}}(z)=
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane given by the
symmetric solution that decays exponentially as we get away from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

Using Eq. \eqref{Eq:J} we can correlate the local current density at
the sample as it is prepared with its geometric and optical
properties. For the calculation of the optical properties we use the
well known transfer matrix method \notaL{refs}.
\notaL{No necesitamos presentar la teoría de matrices de
  transferencia. No hay nada original ahí.}

@@

\notaL{Cambié el título, pues tienes una mezcla de experimento y
  teoría aquí}
In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{Cambié las figuras}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a gold plate \notaL{Lo inventé; de qué material es
  el contacto bajo la muestra} which together make the anode. The
catode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the width, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{Controlaste/mediste la temperatura?} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
  electrodo?} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
platinum wire that with an approximate diameter of $0.5\text{mm}$.
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \notaL{referencia} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of width $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel \cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}

\subsection{Refraction Index of PS GRIN Single Layers}
\label{sec:refraction-index-ps}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  varepsilon o epsilon para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
\end{eqnarray}
\notaL{Te faltaba la igualdad}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
\label{sec:fabrication-grin-ps}
After characterizing the preparation of single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of widths $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\frac{\lambda_c}{4}$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1} which
we chose as that directly below the point-like electrode. The defect
was chosen as a half-wavelength low index layer of width $d_d$ such that
$n_Ld_L=\lambda_c/2$, and the MC has the
following sequence: $(HL)_6HH(LH )_6$. \notaL{Hay algo mal. La
  película de $\lambda/2$ fue de alto o de bajo índice? En una parte
  dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}
We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{P mayúscula
  es porosidad, o p minúscula. Checar consistencia} $P_H =0.46$, and a
width $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and width
varied, yielding a GRIN MC.

\section{Discussion and Results}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/G123}
  \caption{Normalized current density $j_\perp(z,0,0)/I$ calculated through
    Eq. (\ref{Eq:J}) for a
    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.03\text{cm}$ and width $b=0.62\text{cm}$, for a
    point-like electrode at $\bm r_0=(0.2\text{cm},
    0.4\text{cm},0.96\text{cm})$ (top panel). Normalized current
    along the line $y=?$ (bottom panel). \notaL{qué valor de $y$ usaste para la
      gráfica de abajo?} \notaL{Puse $x_0$
      y $y_0$ que faltaban. Checale. Se me hace raro que no esté
      centrado en la celda a lo ancho. ¿No está debería estar en
      $y_0=0.31\text{cm}?$} \notaL{Cambia los letreros, $J$ por
      $j_\perp$. La ordenada no es a, sino $x$ y la abcisa no es b
      sino $y$}. }
  \label{fig:DR1}
\end{figure}
\notaL{Checar consistencia notación. $x_0$, $y_0$ y $z_0$ en
  minúsculas. Igual $j_\perp$.}
In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for the cell we built
(see Figs. \ref{f:celda} and \ref{fig:DE1}) with length
$a=2.03\text{cm}$ and width $b = 0.62\text{cm}$, the height of the
solution was taken as $c=1\text{cm}$ and we set the tip of the
electrode at $\bm
r_0=(x_0,y_0,z_0)=(0.2\text{cm},0.4\text{cm},0.96\text{cm})$
\notaL{Descuidado. En la figura dice 0.98, no 0.96}.
\notaL{¿Por qué usaste estos valores?}
\notaL{Esto no es interesante: the programming with the
  PERL PDL package and corresponding graph in gnuplot.}
\notaL{¿Qué significa esto?:We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect.}
For these parameters we obtained $ j_\perp/I\sim
0.5-1.2\text{cm}^{-2}$
\notaL{Quité el resto del párrafo pues no entendí nada.}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\usepackage{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{red}+C:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}}\notaL{\sout{Indica el voltaje y la
    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}
    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
  fuente de voltaje}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
and $\phi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \phi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

  \nabla^2\phi=-4\pi q_0\delta(\bm r-\bm r_0),

@@

  \phi(x,y,0)=0,

@@

\notaL{\sout{ref}}. The potential within the electrolytic cell coincides

@@

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique \cite{T3,T4,T5}\notaL{\sout{ref}}, which yields
 two rapidly convergingseries, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which there are no
real nor image charges, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors, and then sum over the charges that form the basis
of the 2D {\em crystal} plane and finally sum over all the
 planes \cite{T6,T7} \notaL{\sout{ref}}.
We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{\sout{Checar consistencia entre phi y varphi en todos lados}}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{_{\bm G}}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{_{\bm G}}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{\sout{El signo estaba mal. Chécalo.}} \notaC{En efecto el sino 
estaba mal yo tenia +, y es - por la ecuacion de segundo orden que sale en este caso, tenia tambien 
derivadas parciales y son totales}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane given by the
symmetric solution that decays exponentially as we get away from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

Using Eq. \eqref{Eq:J} we can correlate the local current density at
the sample as it is prepared with its geometric and optical
properties. For the calculation of the optical properties we use the
well known transfer matrix method \notaL{refs}.
\notaL{\sout{No necesitamos presentar la teoría de matrices de
  transferencia. No hay nada original ahí.}}

@@

\notaL{\sout{Cambié el título, pues tienes una mezcla de experimento y
  teoría aquí}}
In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{\sout{Cambié las figuras}}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a metal plate \notaC{\sout{gold plate} error de escritura} 
\notaL{\sout{Lo inventé; de qué material es el contacto bajo la muestra}}
 which together make the anode. The catode consists of a platinum wire 
 insulated except for a small region at its tip, which we take as a 
 point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the width, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{Controlaste/mediste la temperatura?} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaC{Estan son las coordenadas del electrodo} The coordinates the tip of the
electrode at $\bm
r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.3\text{cm},0.9\text{cm})$
\notaL{\sout{¿Cuáles fueron las coordenadas del
  electrodo?}} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
platinum wire that with an approximate diameter of $0.5\text{mm}$.
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \cite{T8,T9} \notaL{\sout{referencia}} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}\notaL{\sout{referencias}}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of width $d$.
\notaL{\sout{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}} \notaC{No tenia ninguna relevancia en este 
punto de la discusión, y si fue una equivocación dejarla hasta el 
final}

\subsection{Refraction Index of PS GRIN Single Layers}
\label{sec:refraction-index-ps}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  $\varepsilon o \epsilon$ para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
\end{eqnarray}
\notaL{Te faltaba la igualdad}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
\label{sec:fabrication-grin-ps}
After characterizing the preparation of single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of widths $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\frac{\lambda_c}{4}$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1} which
we chose as that directly below the point-like electrode. The defect
was chosen as a half-wavelength low index layer of width $d_d$ such that
$n_Hd_H=\lambda_c/2$ \notaC{$n_Ld_L=\lambda_c/2$ error y
 descuido de escritura.} and the MC has the
following sequence: $(HL)_6HH(LH )_6$. \notaL{\sout{Hay algo mal. La
  película de $\lambda/2$ fue de alto o de bajo índice? En una parte
  dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}}
We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{\sout{P mayúscula
  es porosidad, o p minúscula. Checar consistencia}} $p_H =0.46$, and a
width $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $p_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and width
varied, yielding a GRIN MC.
